---
output:
  github_document:
    html_preview: false
---

# funky

<!-- badges: start -->
[![GitHub last commit](https://img.shields.io/github/last-commit/a-maldet/funky.svg?logo=github)](https://github.com/a-maldet/funky/commits/master)
[![GitHub code size in bytes](https://img.shields.io/github/languages/code-size/a-maldet/funky.svg?logo=github)](https://github.com/a-maldet/funky)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```


This **R package** makes **functional programming**
easy and helps avoiding
**memory leaks** when using **closures** in R.

> Functional Programming In R Should Be FunKy

## Installation

```{r}
# Install development version from GitHub
devtools::install_github('a-maldet/funky', build_opts = NULL)
```

## Usage

```{r}
library(funky)
```

## Available functions

- `restrict_fn_env()`: Restrict the environment of a function to the
  **optimal scope** and reduce its ancestry tree to the minimum. This
  is very important, because otherwise the functions created inside of a
  **closure** reference the **entire environment ancestry tree**.
  This may cause **memory leaks** and slow down your code.
- `eval_closure()`: A wrapper for `restrict_fn_env()`, which allows
  you to evaluate an expression inside of a closure, which has the
  **optimal scope**. This is important to **avoid memory leaks** when using
  **closures** in R.
- `get_call_args()`: Returns a named list holding all argument values of the
  current function call (including non-overwritten default values).
- `set_fn_defaults()`: Set the defaults for a given function. Can be useful
  for customizing various functions.
- `get_defaults()`: Return all function arguments including their default
  values for a given function.
  
## Remark:

If you like this package, please give me a star on github:
[https://github.com/a-maldet/funky](https://github.com/a-maldet/funky)

## License

GPL-3